\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-13 methodology.tex
updates to section 4

  [Cold] // cold state: repaired
  [OnEvent(NotifyEnFailure, ProcessExtentNodeFailure)]
  state Repaired : MonitorState {
    void ProcessExtentNodeFailure()
    {
        var node = GetExtentNode(this.Payload);
        ExtentNode2Replica.Remove(node);
        goto Repairing;
    }
  }

  [Hot] // hot state: repairing
  [OnEvent(NotifyExtentRepaired, ProcessExtentRepaired)]
  state Repairing : MonitorState {
    void ProcessExtentRepaired()
    {
      var node = GetExtentNode(this.Payload);
      ExtentNode2Replica[node] = true;

      if (ReplicaCount == Harness.REPLICA_COUNT_TARGET)
        goto Repaired;
    }
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{The RepairMonitor machine.}
\label{fig:monitor}
%\vspace{-2mm}
\end{figure}

>>>>

  // cold state: repaired
  [OnEvent(NotifyEnFailure, ProcessExtentNodeFailure)]
  cold state Repaired : MonitorState {
    void ProcessExtentNodeFailure() {
        var node = GetExtentNode(this.Payload);
        ExtentNode2Replica.Remove(node);
        goto Repairing;
    }
  }

  // hot state: repairing
  [OnEvent(NotifyExtentRepaired, ProcessExtentRepaired)]
  hot state Repairing : MonitorState {
    void ProcessExtentRepaired() {
      var node = GetExtentNode(this.Payload);
      ExtentNode2Replica[node] = true;
      if (ReplicaCount == Harness.REPLICA_COUNT_TARGET)
        goto Repaired;
    }
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{The RepairMonitor machine.}
\label{fig:monitor}
%\vspace{-2mm}
\end{figure}

### 2015-09-13 paper.tex
added a section on exemplary case, partially through methodology
updates
update draft.pdf
some updates all around
various updates
Small change.
updates to section 4

\usepackage{color}
\newcommand{\SQComment}[1]{\textcolor{red}{Shaz: #1}}
\newcommand{\PDComment}[1]{\textcolor{blue}{Pantazis: #1}}
\newcommand{\MMComment}[1]{\textcolor{cyan}{Matt: #1}}
\newcommand{\SCComment}[1]{\textcolor{magenta}{Shuo: #1}}

@@

\lstset{language=[Sharp]C,
showspaces=false,
showtabs=false,
breaklines=true,
showstringspaces=false,
breakatwhitespace=true,
escapeinside={(*@}{@*)},
commentstyle=\color{greencomments},
keywordstyle=\color{bluekeywords}\bfseries,
stringstyle=\color{redstrings},
basicstyle=\ttfamily\scriptsize,
columns=fullflexible
}

@@

\section{Testing Distributed Systems}
\label{sec:bg}

\input{background}

\section{Case Studies in Microsoft}
\label{sec:cases}

\input{casestudies}

\section{Testing Production Systems with \psharp}
\label{sec:method}

@@

\section{The \psharp Bug-Finding Runtime}
\label{sec:psharp}

>>>>

\usepackage{color}
\definecolor{light-gray}{gray}{0.40}
\newcommand{\SQComment}[1]{\textcolor{red}{Shaz: #1}}
\newcommand{\PDComment}[1]{\textcolor{blue}{Pantazis: #1}}
\newcommand{\MMComment}[1]{\textcolor{cyan}{Matt: #1}}
\newcommand{\SCComment}[1]{\textcolor{magenta}{Shuo: #1}}
\newcommand{\CHComment}[1]{\textcolor{blue}{Cheng: #1}}
\newcommand{\PTComment}[1]{\textcolor{light-gray}{Paul: #1}}

@@

\lstset{language=[Sharp]C,
showspaces=false,
showtabs=false,
breaklines=true,
showstringspaces=false,
breakatwhitespace=true,
escapeinside={(*@}{@*)},
morekeywords={OnEvent, nameof, var, state, cold, hot},
commentstyle=\color{greencomments},
keywordstyle=\color{bluekeywords}\bfseries,
stringstyle=\color{redstrings},
basicstyle=\ttfamily\scriptsize,
columns=fullflexible
}

@@

\section{Motivating Example}
\label{sec:motivation}

\input{motivation}

\section{Testing Distributed Systems}
\label{sec:overview}

\input{overview}

\section{Testing Azure Storage vNext with \psharp}
\label{sec:method}

@@

\section{The \psharp Systematic Testing Engine}
\label{sec:psharp}
